Ogrenci Isleri application is both a web application project and a mobile application project for a cafe located in Denizli.

The Ogrenci Isleri application is a mobile application that allows us to create a variety of social events such as trivia competitions at the cafe, theater performances, movie nights, and meet and greet breakfasts. This application also allows customers to view the menu using a QR code, place orders, and pay their bill without going to the cashier.

If we consider the objectives of the Ogrenci Isleri application, the first aim is to try to save the cafe owner from the cost of printing the menu when there is a change in the menu. The second aim is to try to save the cafe owner from excessive labor.

If we consider the importance of the Ogrenci Isleri application, the first importance is that maximum efficiency will be achieved with minimum labor through the process of events related to the application. The second importance is that the minimum cost will result in maximum profit as the customer can view the menu through the QR code. The third importance is that the customer will be spared from spending time in front of the cashier.

If we consider the differences between the Ogrenci Isleri project and other projects, the first difference is that other applications are only mobile applications, whereas the Ogrenci Isleri project is both a mobile application and a web application. The second difference is that other applications only allow for operations related to tables and menus, whereas the Ogrenci Isleri project also allows for many operations such as viewing events, creating new events, and participating in events.

The technologies I will use to develop the Ogrenci Isleri application are as follows: I will use React Native for the frontend of the mobile application and React for the frontend of the web application. I will use Firebase to develop the backend of both the mobile and web applications. The main reason for choosing these technologies is that they are very popular today and therefore have a lot of resources available.

The database of the project will contain the following data: User information (Name - Surname, Phone number, Email address...) / Does the user want to create an event or participate in an event? / What kind of event does the user want to organize? (Meeting, Breakfast, Game...) / What event did the user come to? (Trivia competition, Theater performance...) / Did they come as a group or alone? / Group information (Group name, Number of people...) / Menu data (Category of the product, Name of the product, Price of the product...)

\textbf{Keywords:} Mobile application, Web application, Social events, Application, Menu, QR code, Maximum profit, Minimum labor, React Native, React, Firebase, Data.